AIMS DataPlatform R Client Notebook Example

### 2019-08-22 docs/detailed-example.Rmd
Update docs
Update links

---
title: "AIMS DataPlatform R Client Notebook Example"
output: html_notebook
---

This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index) to see what that means.

Similar to our previous example we want to run a plot on a series, lets discover a series to plot.

>>>>

---
title: "AIMS DataPlatform R Client Notebook Example"
output: html_notebook
---
[Back](index)

This example assumes you have stored an *AIMS DataPlatform API Key* in your `.Renviron` file.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.

Similar to our previous example we want to run a plot on a series, lets discover a series to plot.  If you are running this notebook in [R Studio](https://www.rstudio.com/) you can click on the green arrow inside each code block to run it.
